Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
mention north Galactic pole f_1 features, reference f_1 maps from text

The resulting full-sky map of $f_1$ is shown in Figure \ref{}. Some of the most

>>>>

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. Some of 
the most striking features occurr near the north Galactic pole, and to 
highlight these regions of unusually high $f_1$, we display the northern
Galactic hemisphere in Lambert projection in Figure \ref{fig:f1lambert}.
